Black-hole ringdown as a probe of higher-curvature gravity theories

### 2022-04-12 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
hs: swapped acknowledgements / appendix order
hs: added a first version of the abstract

%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
% General
% Motivation
% What we do
% Main conclusion
\end{abstract}
%%%%%%%%%%%%%%%%%%%%%%%

@@

@@

\section{Details of the determination of the theory-specific
ParSpec coefficients}
\label{app:map_details}
\agcomm{Reorder sections, such that the appendix comes after the Acknowledgments?}

@@

%%%%%%%%%%%%%%%%%
\section*{Acknowledgements}
\label{sec:acknowledgements}
%
We thank Emanuele Berti, Andrea Maselli, Caio F. B. Macedo, Deyan Mihaylov,
Serguei Ossokine, Scott E. Perkins, and Helvi Witek for discussions.
%
We are grateful for the computational resources provided by the Max Planck
Institute for Gravitational Physics in Potsdam, specifically the
high-performace computing cluster Hypatia and to Steffen Grunewald for
assistance.
%
The authors would like to thank everyone at the frontline of the Covid-19
pandemic.
%%%%%%%%%%%%%%%%%

>>>>

%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
% General:
The detection of gravitational waves produced by coalescing compact binaries
allows us to explore the dynamical, nonlinear regime of general relativity
and to constrain modifications to it.
%
Some of these gravitational-wave events are detected with sufficiently high
signal-to-noise ratio, allowing us to probe the relaxation of the remnant black
hole to its final, stationary state -- the so-called black-hole ringdown,
characterized by a set of quasinormal modes.
% Main question:
Can we use the ringdown to constrain deviations to general relativity,
as predicted by several of its contenders?
% What we do:
Here, we take a first step to address this question, by using an
inspiral-merger-ringdown waveform model in the effective-one-body formalism,
augmented with a parametrization of the ringdown based on an expansion on the
final black hole's spin.
%
We give a prescription on to include to this waveform model the quasinormal mode frequencies
calculated on a theory-by-theory basis, in particular, for theories that deviate
from general relativity through higher-curvature corrections, namely,
Einstein-dilaton-Gauss-Bonnet, dynamical Chern-Simons, cubic- and quartic-order
effective-field-theories of general relativity.
%
% Main conclusion:
We confront the resultant waveform models against GW150914 and GW200129 data,
finding that while Einstein-dilaton-Gauss-Bonnet cannot be constrained with
these events, we can place upper bounds on the coupling constants of cubic-
($\ell_{\rm cEFT} \leqslant 38.2$~km) and quartic-order ($\ell_{\rm qEFT}
\leqslant 51.3$~km) effective-field-theories of general relativity, and
of dynamical Chern-Simons gravity ($\ell_{\rm CS} \leqslant 38.7$~km).
%
The latter result constitutes a concrete example of a theory presently
unconstrained by inspiral-only analyses which, however, can be constrained by
merger-ringdown studies.
\end{abstract}
%%%%%%%%%%%%%%%%%%%%%%%

@@

% --------------------------
\section*{Acknowledgements}
\label{sec:acknowledgements}
%
We thank Emanuele Berti, Andrea Maselli, Caio F. B. Macedo, Deyan Mihaylov,
Serguei Ossokine, Scott E. Perkins, and Helvi Witek for discussions.
%
We are grateful for the computational resources provided by the Max Planck
Institute for Gravitational Physics in Potsdam, specifically the
high-performace computing cluster Hypatia and to Steffen Grunewald for
assistance.
%
The authors would like to thank everyone at the frontline of the Covid-19
pandemic.
% --------------------------

@@

\section{Details of the determination of the theory-specific
ParSpec coefficients}
\label{app:map_details}
% HS: done.
% \agcomm{Reorder sections, such that the appendix comes after the Acknowledgments?}

@@
